Recovering from population extinction in the Animal Life Cycle Algorithm (ALCA)

### 2022-09-23 paper.tex
Updated Experiments
Work in progress.

\subsubsection{Experiment 1} The goal of our first OneMax experiment was to
make sure our Life-Cycle algorithm worked as expected, converging on the
solution. For this experiment, we intentionally used delays (on the tenth of a
second magnitude) to follow the Life-Cycle algorithm behavior on the console
output. For this experiment, we compared the DEAP algorithm versus the
Life-Cycle using ten processes (on containers) where we show the summarized
results in Table~\ref{tab.experiment1}, and Figure~\ref{fig.experiment1} shows
their Box and Whisker chart.

\begin{table}[]
    \centering        
    \caption{Experiment 1 results: OneMax DEAP versus Life-Cycle (10 processes).}\label{tab.experiment1}
    \begin{tabular}{|l|l|l|l|l|l|l|l|l|}
    \hline
    Run & \multicolumn{4}{l|}{OneMax DEAP} & \multicolumn{4}{l|}{Life-Cycle (10P)} \\ \hline
    1-60 & Last Gen. & Eval. & Time (sec) & Eval/sec & Last Gen. & Eval. & Time (sec) & Eval/sec \\ \hline
    Avg. & 6.5 & 391 & 0.036 & 10,836 & 9.6 & 578 & 6.830 & 85 \\ \hline
    \end{tabular}
    \end{table}

\begin{figure}
    \fbox{\includegraphics[width=\textwidth]{img/fig6_experiment01_chart.pdf}}
    \caption{Box and whisker chart for the Experiment 1: OneMax DEAP versus Life-Cycle.} \label{fig.experiment1}
% You need to label axis y - JJ
  \end{figure}

\subsubsection{Experiment 2} The goal of our second experiment was to confirm
the Life-Cycle algorithm continued working as expected, converging on the
solution. For this experiment, we reduced the time used on delays (now on the
thousands of a second magnitude) to follow the Life-Cycle algorithm behavior.
For this experiment, we only used tournament selection for the reproduction, on
the first configuration running the Life-Cycle on ten processes, versus the
second configuration where we reduced the processes to the minimum basic 5. We
show the summarized results in Table~\ref{tab.experiment2}, and
Figure~\ref{fig.experiment2} shows their Box and Whisker chart.

\begin{table}[]
    \centering        
    \caption{Experiment 2 results, Life-Cycle Tournament selection: 10 versus 5 processes.}\label{tab.experiment2}
    \begin{tabular}{|l|l|l|l|l|l|l|l|l|}
    \hline
    Run & \multicolumn{4}{l|}{LifeCycle (Tourn. 10P)} & \multicolumn{4}{l|}{LifeCycle (Tourn. 5P)} \\ \hline
    1-60 & Last Gen. & Eval. & Time (sec) & Eval/sec & Last Gen. & Eval. & Time (sec) & Eval/sec \\ \hline
    Avg. & 7.2 & 434 & 0.740 & 587 & 8.2 & 495 & 0.826 & 599 \\ \hline
    \end{tabular}
    \end{table}

\begin{figure}
    \fbox{\includegraphics[width=\textwidth]{img/fig7_experiment02_chart.pdf}}
    \caption{Box and Whisker chart for the Experiment 2: Life-Cycle Tournament selection (10 versus 5 processes).} \label{fig.experiment2}
    \end{figure}

\subsubsection{Experiment 3} The goal of our third experiment was to follow and
study the behavior of the Life-Cycle algorithm that continued converging on the
solution. For this experiment, we remained using minimal delays (thousands of a
second magnitude). For this experiment, we only used tournament selection for
the reproduction, on the first configuration running the Life-Cycle on six
processes, two of whom was the Death process, versus the second configuration
where we reduced the processes to the minimum (five) but increasing the (Death)
goal approval range to 115. We show the summarized results in
Table~\ref{tab.experiment3}, and Figure~\ref{fig.experiment3} shows their Box
and Whisker chart.

\begin{table}[]
    \centering        
    \caption{Experiment 3 results, Life-Cycle Tournament: 6 processes (Death x2) versus 5 processes (80 to 115 goal).}\label{tab.experiment3}
    \begin{tabular}{|l|l|l|l|l|l|l|l|l|}
    \hline
    Run & \multicolumn{4}{l|}{LifeCycle (Tourn. 6P, Death x2)} & \multicolumn{4}{l|}{LifeCycle (Tourn. 5P, 80-115g)} \\ \hline
    1-60 & Last Gen. & Eval. & Time (sec) & Eval/sec & Last Gen. & Eval. & Time (sec) & Eval/sec \\ \hline
    Avg. & 8.0 & 483 & 0.846 & 571 & 6.4 & 384 & 0.695 & 553 \\ \hline
    \end{tabular}
    \end{table}

\begin{figure}
    \fbox{\includegraphics[width=\textwidth]{img/fig8_experiment03_chart.pdf}}
    \caption{Box and Whisker chart for the Experiment 3: Life-Cycle Tournament (6 processes double Death, versus 5 processes with an 80 to 115 goal approval).} \label{fig.experiment3}
    \end{figure}

\subsubsection{Experiment 4} The goal of our fourth and last experiment was to
follow and study the behavior of the Life-Cycle algorithm that continued
converging on the solution. For this experiment, we remained using minimal
delays (thousands of a second magnitude). For this experiment, we compared the
OneMax DEAP implementation versus the Life-Cycle algorithm, only using
tournament selection for the reproduction, with the Life-Cycle configuration
running on the minimum (five) processes but increasing the (Death) goal
approval range to 125. We show the summarized results in
Table~\ref{tab.experiment4}, and Figure~\ref{fig.experiment4} shows their Box
and Whisker chart.

\begin{table}[]
    \centering        
    \caption{Experiment 4 results, OneMax DEAP versus Life-Cycle Tournament: 5 processes (80 to 125 goal).}\label{tab.experiment4}
    \begin{tabular}{|l|l|l|l|l|l|l|l|l|}
    \hline
    Run & \multicolumn{4}{l|}{OneMax DEAP} & \multicolumn{4}{l|}{Life-Cycle (Tourn. 5P, 80-125g)} \\ \hline
    1-60 & Last Gen. & Eval. & Time (sec) & Eval/sec & Last Gen. & Eval. & Time (sec) & Eval/sec \\ \hline
    Avg. & 6.5 & 391 & 0.036 & 10,836 & 6.3 & 377 & 0.678 & 556 \\ \hline
    \end{tabular}
    \end{table}

\begin{figure}
    \fbox{\includegraphics[width=\textwidth]{img/fig9_experiment4_chart.pdf}}
    \caption{Box and Whisker chart for the Experiment 4: OneMax DEAP versus Life-Cycle Tournament (5 processes with an 80 to 125 goal approval).} \label{fig.experiment4}
    \end{figure}

>>>>

\subsubsection{Experiment 1} The goal of our first OneMax experiment was to
make sure our Life-Cycle algorithm worked as expected, converging on the
solution. For this experiment, we intentionally used delays (on the tenth of a
second magnitude) to follow the Life-Cycle algorithm behavior on the console
output. For this experiment, we compared the DEAP algorithm versus the
Life-Cycle using ten processes (on containers) where we show the summarized
results in Table~\ref{tab.fun_ackley5}, and Figure~\ref{fig.fun_ackley} shows
their Box and Whisker chart.

\subsubsection{Experiment 2} The goal of our second experiment was to confirm
the Life-Cycle algorithm continued working as expected, converging on the
solution. For this experiment, we reduced the time used on delays (now on the
thousands of a second magnitude) to follow the Life-Cycle algorithm behavior.
For this experiment, we only used tournament selection for the reproduction, on
the first configuration running the Life-Cycle on ten processes, versus the
second configuration where we reduced the processes to the minimum basic 5. We
show the summarized results in Table~\ref{tab.fun_ackley5}, and
Figure~\ref{fig.fun_ackley} shows their Box and Whisker chart.

\subsubsection{Experiment 3} The goal of our third experiment was to follow and
study the behavior of the Life-Cycle algorithm that continued converging on the
solution. For this experiment, we remained using minimal delays (thousands of a
second magnitude). For this experiment, we only used tournament selection for
the reproduction, on the first configuration running the Life-Cycle on six
processes, two of whom was the Death process, versus the second configuration
where we reduced the processes to the minimum (five) but increasing the (Death)
goal approval range to 115. We show the summarized results in
Table~\ref{tab.fun_ackley5}, and Figure~\ref{fig.fun_ackley} shows their Box
and Whisker chart.

\subsubsection{Experiment 4} The goal of our fourth and last experiment was to
follow and study the behavior of the Life-Cycle algorithm that continued
converging on the solution. For this experiment, we remained using minimal
delays (thousands of a second magnitude). For this experiment, we compared the
OneMax DEAP implementation versus the Life-Cycle algorithm, only using
tournament selection for the reproduction, with the Life-Cycle configuration
running on the minimum (five) processes but increasing the (Death) goal
approval range to 125. We show the summarized results in
Table~\ref{tab.fun_ackley5}, and Figure~\ref{fig.fun_ackley} shows their Box
and Whisker chart.
